
# Experiment 1

## Experiment 1a

Eyes

```{r}
df_E1a_clean <- df_E1a_raw %>% 
  filter(isabove200 == 1) %>% 
  select(-isabove200)
```

### Accuracy

```{r}
df_E1a_acc <- df_E1a_clean %>% 
  group_by(SubjCode, Feature, State) %>% 
  summarize(Acc = mean(isCorrect),
            .groups = "drop")
df_E1a_acc
```

```{r}
df_E1a_acc_wide <- df_E1a_acc %>% 
  pivot_wider(id_cols = SubjCode,
              names_from = State,
              values_from = Acc)
df_E1a_acc_wide
```

#### t-test
```{r}
t_E1a_acc <- t.test(df_E1a_acc_wide$open,
                    df_E1a_acc_wide$closed,
                    paired = TRUE,
                    var.equal = TRUE)
t_E1a_acc
```

```{r}
repeated_measures_d(t_E1a_acc)
```

#### RM-ANOVA
Whether the performance varies across the four locations:
```{r}
aov_E1a_acc <- aov_ez(id = "SubjCode",
                      dv = "isCorrect",
                      within = c("State", "Location"),
                      data = df_E1a_clean,
                      fun_aggregate = mean)
aov_E1a_acc
```

```{r}
aov_E1a_acc %>% 
  eta_squared()
```

#### Estimated marginal means

```{r}
emm_E1a_acc <- emmeans(aov_E1a_acc, ~ State * Location)
emm_E1a_acc
```

#### Follow-up analysis

Open vs. closed state:
```{r}
emmeans(aov_E1a_acc, "pairwise" ~ State)
```

```{r}
emmip(aov_E1a_acc, ~State, CIs = TRUE)
```

```{r}
contrast(emm_E1a_acc, "pairwise", simple = "State")[1:4] %>% 
  summary(adjust = "none")
```

```{r}
contrast(emm_E1a_acc, "pairwise", simple = "Location") %>% 
  summary(adjust = "none")
```

```{r}
emmip(aov_E1a_acc, State ~ Location, CIs = TRUE)
```

Location:
- `1`: right top
- `2`: left top
- `3`: left bottom
- `4`: right bottom

### Correct response times

```{r}
df_E1a_rt <- df_E1a_clean %>% 
  filter(isCorrect == 1) %>%
  group_by(SubjCode, Feature, State) %>% 
  summarize(meanRT = round(mean(RT)),
            .groups = "drop")
df_E1a_rt
```

```{r}
df_E1a_rt_wide <- df_E1a_rt %>% 
  pivot_wider(id_cols = SubjCode,
              names_from = State,
              values_from = meanRT)
df_E1a_rt_wide
```

#### t-test
```{r}
t_E1a_rt <- t.test(df_E1a_rt_wide$open,
                    df_E1a_rt_wide$closed,
                    paired = TRUE,
                    var.equal = TRUE)
t_E1a_rt
```

```{r}
# effect size
repeated_measures_d(t_E1a_rt)
```


#### RM-ANOVA

```{r}
aov_E1a_rt <- aov_ez(id = "SubjCode",
                     dv = "RT",
                     within = c("State", "Location"),
                     data = df_E1a_clean %>% 
                       filter(isCorrect == 1),
                     fun_aggregate = mean)
aov_E1a_rt
```

```{r}
aov_E1a_rt %>% 
  eta_squared()
```

#### Estimated marginal means

```{r}
emm_E1a_rt <- emmeans(aov_E1a_rt, ~ State * Location)
emm_E1a_rt
```

#### Follow-up analysis

```{r}
emmeans(aov_E1a_rt, "pairwise" ~ State)
```

```{r}
emmip(aov_E1a_rt, ~State, CIs = TRUE)
```

```{r}
contrast(emm_E1a_rt, "pairwise", simple = "State")[1:4] %>% 
  summary(adjust = "none")
```

```{r}
contrast(emm_E1a_rt, "pairwise", simple = "Location") %>% 
  summary(adjust = "none")
```

```{r}
emmip(aov_E1a_rt, State ~ Location, CIs = TRUE)
```

Location:
- `1`: right top
- `2`: left top
- `3`: left bottom
- `4`: right bottom

## Experiment 1b

Mouth

```{r}
df_E1b_clean <- df_E1b_raw %>% 
  filter(isabove200 == 1) %>%
  select(-isabove200)
```

### Accuracy

```{r}
df_E1b_acc <- df_E1b_clean %>% 
  group_by(SubjCode, Feature, State) %>% 
  summarize(Acc = mean(isCorrect),
            N = n(),
            .groups = "drop")
df_E1b_acc
```

```{r}
df_E1b_acc_wide <- df_E1b_acc %>% 
  pivot_wider(id_cols = SubjCode,
              names_from = State,
              values_from = Acc)
df_E1b_acc_wide
```

#### t-test
```{r}
t_E1b_acc <- t.test(df_E1b_acc_wide$open,
                    df_E1b_acc_wide$closed,
                    paired = TRUE,
                    var.equal = TRUE)
t_E1b_acc
```

```{r}
# effect size
repeated_measures_d(t_E1b_acc)
```

#### RM-ANOVA

```{r}
aov_E1b_acc <- aov_ez(id = "SubjCode",
                      dv = "isCorrect",
                      within = c("State", "Location"),
                      data = df_E1b_clean,
                      fun_aggregate = mean)
aov_E1b_acc
```

```{r}
aov_E1b_acc %>% 
  eta_squared()
```

#### Estimated marginal means

```{r}
emm_E1b_acc <- emmeans(aov_E1b_acc, ~ State * Location)
emm_E1b_acc
```

#### Follow-up analysis

```{r}
emmeans(aov_E1b_acc, "pairwise" ~ State)
```

```{r}
emmip(aov_E1b_acc, ~ State, CIs = TRUE)
```

```{r}
contrast(emm_E1b_acc, "pairwise", simple = "State")[1:4] %>% 
  summary(adjust = "none")
```

```{r}
contrast(emm_E1b_acc, "pairwise", simple = "Location") %>% 
  summary(adjust = "none")
```

```{r}
emmip(aov_E1b_acc, State ~ Location, CIs = TRUE)
```

Location:
- `1`: right top
- `2`: left top
- `3`: left bottom
- `4`: right bottom

### Correct response times

```{r}
df_E1b_rt <- df_E1b_clean %>% 
  filter(isCorrect == 1) %>%
  group_by(SubjCode, Feature, State) %>% 
  summarize(meanRT = round(mean(RT)),
            .groups = "drop")
df_E1b_rt
```

```{r}
df_E1b_rt_wide <- df_E1b_rt %>% 
  pivot_wider(id_cols = SubjCode,
              names_from = State,
              values_from = meanRT)
df_E1b_rt_wide
```

#### t-test
```{r}
t_E1b_rt <- t.test(df_E1b_rt_wide$open,
                    df_E1b_rt_wide$closed,
                    paired = TRUE,
                    var.equal = TRUE)
t_E1b_rt
```

```{r}
# effect size
repeated_measures_d(t_E1b_rt)
```

#### RM-ANOVA

```{r}
aov_E1b_rt <- aov_ez(id = "SubjCode",
                     dv = "RT",
                     within = c("State", "Location"),
                     data = df_E1b_clean %>% 
                       filter(isCorrect == 1),
                     fun_aggregate = mean)
aov_E1b_rt
```

```{r}
aov_E1b_rt %>% 
  eta_squared()
```
#### Estimated marginal means

```{r}
emm_E1b_rt <- emmeans(aov_E1b_rt, ~ State * Location)
emm_E1b_rt
```

#### Follow-up analysis

```{r}
emmeans(aov_E1b_rt, "pairwise" ~ State)
```

```{r}
emmip(aov_E1b_rt, ~ State, CIs = TRUE)
```

```{r}
contrast(emm_E1b_rt, "pairwise", simple = "State")[1:4] %>% 
  summary(adjust = "none")
```

```{r}
contrast(emm_E1b_rt, "pairwise", simple = "Location") %>% 
  summary(adjust = "none")
```

```{r}
emmip(aov_E1b_rt, State ~ Location, CIs = TRUE)
```

Location:
- `1`: right top
- `2`: left top
- `3`: left bottom
- `4`: right bottom

## Experiment 1a & 1b

```{r}
df_E1_clean <- df_E1_raw %>% 
  filter(isabove200 == 1) %>% 
  select(-isabove200)
```

### Accuracy

#### RM-ANOVA

```{r}
aov_E1_acc <- aov_ez(id = "SubjCode",
                     dv = "isCorrect",
                     within = c("State", "Location"),
                     between = "Feature",
                     data = df_E1_clean,
                     fun_aggregate = mean)
aov_E1_acc
```

```{r}
aov_E1_acc %>% 
  eta_squared()
```

#### Estimated marginal means

```{r}
emm_E1_acc <- emmeans(aov_E1_acc, ~ Feature * State * Location)
emm_E1_acc
```

#### Follow-up analysis

```{r}
emmeans(aov_E1_acc, "pairwise" ~ State)
```

```{r}
emmeans(aov_E1_acc, ~ State + Feature) %>% 
  contrast(interaction = "pairwise")
```
Differences between open and closed states does not depend on the feature.

```{r}
contrast(emm_E1_acc, "pairwise", simple = "State")[1:8] %>% 
  summary(adjust = "none")
```

```{r}
contrast(emm_E1_acc, "pairwise", simple = "Location") %>% 
  summary(adjust = "none")
```

#### Plot

```{r}
emmip(aov_E1_acc, State ~ Feature, CIs = TRUE) +
  labs(y = "Accuracy")
```

```{r}
emmip(aov_E1_acc, State ~ Feature | Location, CIs = TRUE) +
  labs(y = "Accuracy")
```

Location:
- `1`: right top
- `2`: left top
- `3`: left bottom
- `4`: right bottom

### Correct response times

#### RM-ANOVA

```{r}
aov_E1_rt <- aov_ez(id = "SubjCode",
                    dv = "RT",
                    within = c("State", "Location"),
                    between = "Feature",
                    data = filter(df_E1_clean,
                                  isCorrect == 1),
                    fun_aggregate = mean)
aov_E1_rt
```

```{r}
aov_E1_rt %>% 
  eta_squared()
```

#### Estimated marginal means

```{r}
emm_E1_rt <- emmeans(aov_E1_rt, ~ State * Location * Feature)
emm_E1_rt
```

#### Follow-up analysis

```{r}
emmeans(aov_E1_rt, "pairwise" ~ State)
```

```{r}
emmeans(aov_E1_rt, ~ State + Feature) %>% 
  contrast(interaction = "pairwise")
```

```{r}
contrast(emm_E1_rt, "pairwise", simple = "State")[1:8] %>% 
  summary(adjust = "none")
```

```{r}
contrast(emm_E1_rt, "pairwise", simple = "Location") %>% 
  summary(adjust = "none")
```

#### Plot

```{r}
emmip(aov_E1_rt, State ~ Location | Feature, CIs = TRUE) +
  labs(y = "correct Response Times (ms)")
```
Location:
- `1`: right top
- `2`: left top
- `3`: left bottom
- `4`: right bottom
